---
title: "Income Tax Data Project"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  pdf_document: default
  html_document: default
urlcolor: blue
---

# Introduction 

Integrated Data Division (CITZ) has acquired historical annual t1 tax data from BC Stats (JTT) who has in turn purchased the data tables from Statistics Canada.

The data are in .xls format and are housed in the folder named Individuals xls and Family xls

In this project, the xls files are cleaned and merged into one csv sheet per year using open source RStudio. The cleaned data are in Provincial Extract folder and the codes used to wrangle the data are within R script folder respectively.

The BC Gov GitHub repository about this project can found here: https://github.com/bcgov/statscan-taxdata-tidying

The technical Reference Guide for the Annual Income Estimates for Census Families, Individuals and Seniors can be found in the `/Documentation` folder. For information about this product or the wide range of services and data available from Statistics Canada, visit their [website](www.statcan.gc.ca).
For further questions, the Statistics Canada email is <STATCAN.infostats-infostats.STATCAN@canada.ca>. 


This data (from Statistics Canada) includes information copied with permission from Canada Post Corporation. Information about Statistics Canada Open Licence Grants can be found here: https://www.statcan.gc.ca/eng/reference/licence 

# Data table structures for individuals and families

Currently, the fully anonymized data includes income estimates for individuals ranging from years 2000 up to 2015. Each table in a year is an aggregation of sub-tables as listed in Table 1. The anonymized income estimates for families range from years 2004 up to 2016. Each table in a year is an aggregation of all sub-tables as listed in Table 2. 

The original data came in xls format with spaces in names. They were opened in microsoft excel and their names were fixed with no space and re-saved as xlsx. RStudio was then used to wrangle the data into machine readable csv's. 


```{r echo= FALSE}
library(knitr)
library(kableExtra)
Individuals <- data.frame(
  # = 1:19,	
  
  Table_ID = c("Table I-01", "Table I-02", "Table I-3A", "Table I-3B", "Table I-3C", "Table I-04", "Table I-5A", "Table I-5B",
            "Table I-5C", "Table I-06", "Table I-7A", "Table I-7B", "Table I-7C", "Table I-08", "Table I-09", "Table I-10",
            "Table I-11", "Table I-12", "Table I-13"), 
  
  Table_Name = c("Taxfilers and dependents, summary table, income and demographics of individuals", "Taxfilers and dependents by sex, marital status and age groups", "Male taxfilers and dependents by single years of age", "Female taxfilers and dependents by single years of age", "Taxfilers and dependents by single year of age", "Taxfilers and dependents with income by source of income", "Male taxfilers and dependents with income by total Income and age groups", "Female taxfilers and dependents with income by total income and age groups", "Taxfilers and dependents with income by total income and age groups", "Taxfilers and dependents with income by sex, income taxes, selected deductions and benefits", "Male taxfilers and dependents with income by after-tax income and age groups", "Female taxfilers and dependents  with income by after-tax income and age groups", "Taxfilers and dependents with income by after-tax income and age groups", "Taxfilers and dependents with income by income taxes and after-tax income, sex and age groups", "Economic dependency profile of individuals", "Labour income profile of individuals", "Taxfilers and dependents 15 years of age and over with labour income by sex and age groups", "Taxfilers and dependents 15 years of age and over receiving employment insurance by age groups and sex", "After-tax low income status of tax filers and dependents, census family low income measure, for couple and lone parent families by family composition"),																																																																											
 stringsAsFactors = FALSE)
``` 


```{r echo = FALSE}
kable(cbind(Individuals), "latex", booktabs = T, caption = "Structure for Individual Tables") %>%
  kable_styling(latex_options = c("striped", "scale_down", font_size=200))
```


```{r echo= FALSE}
library(knitr)
library(kableExtra)
Family <- data.frame(
  # = 1:26,	
  
  Table_ID = c("Table F-01", "Table F-02", "Table F-3A", "Table F-3B", "Table F-3C", "Table F-04A", "Table F-04B", "Table F-04C", "Table F-5A", "Table F-5B", "Table F-06", "Table F-7", "Table F-08", "Table F-09", "Table F-10", "Table F-11", "Table F-12", "Table F-13", "Table F-14A", "Table F-14B", "Table F-14C", "Table F-15", "Table F-17", "Table F-18", "Table F-19", "Table F-20"),
  
  Table_Name = c("Summary census family income table", "Taxfilers and dependents by age groups and census family type", "Couple families by age of older partner or parent and number of children", "Lone-Parent families by age of parent and number of children", "Census families by age of older partner or parent and number of children", "Distribution of total income by couple family and age of older partner or parent", "Distribution of total income by lone-parent family and age of parent", "Distribution of total income of persons not in census families by age of individual", "Couple families by total income and number of children", "Lone-Parent families by total income and number of children", "Sources of Income by census family Type", "Economic dependency profile of couple families", "Economic dependency profile of lone-parent families and persons not in census families", "Labour income profile of couple families", "Labour income profile of lone-parent families and persons not in census families", "Labour income by age group and sex", "Employment insurance by age group and sex", "Single-earner and dual-earner families by number of children, includes only partners, parents reporting non-negative employment income", "Couple families by percentage of wife's contribution to couple's employment income and by number of children", "Couple families by percentage of wife's contribution to husband/wife employment income and by age of wife", "Couple families by percentage of wife's contribution to husband, wife employment income and by family employment income range", "Census families with children by age of children and children by age groups", "Before-tax low income status, based on census family low income measures, family type and family composition", "After-tax low income status, based on census family low income measures, by family type and family composition", "After-tax low income status of census families, census family low income measures, by family type and family composition, adjusted methodology", "Census families by family type and family composition including before and after-tax median income of the family"),
  
  
 stringsAsFactors = FALSE)
``` 


```{r echo = FALSE}
kable(cbind(Family), "latex", booktabs = T, caption = "Structure for Family Tables") %>%
  kable_styling(latex_options = c("striped", "scale_down", font_size=200))
```
